---
title: "DA Exercises"
author: "Hira Piracha"
output:
  pdf_document: default
  html_document: default
---
##Exercicse 1.1
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(ggplot2)
library(plyr)
```


```{r vienna-hotels}
getwd()
hotels_vienna <- read.csv(file="/Users/hirapiracha/R-Coding1/hotels-vienna.csv", header=TRUE, sep=",")
```

**1.)**
```{r sample 1}
Test1 <- hotels_vienna[sample(nrow(hotels_vienna), 25), ]
(Average_1 = mean(Test1$price, na.rm = TRUE))
```

**2.**
```{r sample 2}
Test2 <- hotels_vienna[sample(nrow(hotels_vienna), 50), ]
(Average_2 = mean(Test2$price, na.rm = TRUE))
```

**3.**
```{r sample 3}
Test3 <- hotels_vienna[sample(nrow(hotels_vienna), 200), ]
(Average_3 = mean(Test3$price, na.rm = TRUE))
```

**4.**
```{r sample 4}
(Average_4 = mean(hotels_vienna$price, na.rm = TRUE))
```

#Summary: The outcomes were different each time I ran the sample. 
#There is a price differene between between the average hotel prices of the data and the sampling. However, more testing is needed for further analysis. 

##Exercise 2.5

```{r}
library(dplyr)
epl_games <- read.csv(file="/Users/hirapiracha/R-Coding1/epl_games.csv", header=TRUE, sep=",")
head(epl_games)
```

cols(
  div = col_character(),
  season = col_double(),
  date = col_character(),
  team_home = col_character(),
  team_away = col_character(),
  points_home = col_double(),
  points_away = col_double(),
  sgoals_home = col_double(), 
  goals_away = col_double()
)
```{r}
st2 <- epl_games %>% group_by(team_home) %>% 
  filter(n_distinct(season) == 11) %>%
  summarise(team_home, season)

#Teams that played in all seasons:
#Arsenal
#Everton
#Chelsea
#Man United
#Liverpool
#Tottenham
#Man City
```

```{r}
st3 <- epl_games %>% group_by(team_home) %>% 
  filter(n_distinct(season) == 1) %>%
  summarise(team_home, season)

#Teams that only played once

#Blackpool
#Reading
```

